State of the Art Review on Privacy-Preserving Authentication

### 2022-01-15 prism-backend/research/soa_review/ac.tex
Added section on real-world deployments of ACs.

\paragraph{Revocation.} %
Perhaps surprisingly, revocation is not a common functionality, although it is
certainly considered by several works, e.g. \cite{cl01,cks10,ckl+15}, and for
some it is just sketched \cite{hs21}.

@@

\begin{itemize}
\item Idemix.
\item Hyperledger Indy.
\item U-Prove.
\end{itemize}

>>>>

\paragraph{Revocation.} %
Perhaps surprisingly, revocation is not a common functionality, although it is
certainly considered by several works, e.g. \cite{cl01,cks10,ckl+15,bran00}, and
for some it is just sketched \cite{hs21}.

@@

Anonymous credential systems saw a first phase of real world deployment during
the first years of the 2010s, mostly through IBM's Idemix%
\footnote{\url{https://idemix.wordpress.com/} (last access, January 15th, 2022).}
and Microsoft's U-Prove%
\footnote{\url{https://www.microsoft.com/en-us/research/project/u-prove/} (last
access, January 15th, 2022).}. Idemix is based on the CL line of works, and
thus inherits their security and privacy properties (multi-show, selective
disclosure). U-Prove is based on on Brands's work, and thus it features
one-show credentials with selective disclosure. Both approaches also support
proving, in zero-knowledge, arbitrary predicates on the credentials' attributes
(albeit with linear costs). \todo{Verify the last claim -- they do, but I'm not
  sure if this is specified in their corresponding papers.}

In the late 2010s, anonymous credential systems started receiving increased
attention by the industry, as a consequence of the W3C's Decentralised
Identities%
\footnote{\url{https://www.w3.org/TR/did-core/} (last access, January 15th, 2022).}
and Verifiable Credentials%
\footnote{\url{https://www.w3.org/TR/vc-data-model/} (last access, January 15th,
  2022).} initiatives, associated to the blockchain world. Idemix made its way
into Hyperldedger Fabric%
\footnote{See \url{https://hyperledger-fabric.readthedocs.io/en/release-2.2/idemix.html} (last access, January 15th, 2022).}
, which since version 1.3 allows the distribution of Idemix credentials
(although they have migrated from CL-based credentials to BBS+-based ones).
Also within the umbrella of the Hyperledger consortium, we can find Indy
\needcite, which directly focuses on digital identity (as opposed to Fabric,
which is a general-purpose permissioned blockchain system). Indy is, in turn,
the evolution of Sovrin%
\footnote{\url{https://sovrin.org/} (last access, January 15th, 2022).}, one of
the main proponents of verifiable credentials, building on CL anonymous credentials%
\footnote{Note, as opposed to Idemix, which migrated to BBS+ credentials,
  Indy/Sovrin seems to stick to CL credentials, according to online
  documentation \url{https://hyperledger-indy.readthedocs.io/projects/hipe/en/latest/text/0109-anoncreds-protocol/README.html} (last access, January 15th, 2022).}
Indy has related subprojects Aries%
\footnote{\url{https://www.hyperledger.org/use/aries} (last access, January
  15th, 2022.)} and Ursa%
\footnote{\url{https://www.hyperledger.org/use/ursa} (last access, January 15th,
  2022).}; Aries deals
with other layers of the approach to credential systems defined by the W3C's
VC initiative, and Ursa is the library implementing the underlying cryptographic
primitives (e.g., CL signatures). With respect to W3C's DID and VC initiatives,
the one that is closely related to anonymous credentials is VC. Basically, this
is a set of specifications that define how to represent digital credentials and
their associated processes. Having been heavily influenced by the literature
on anonymous credentials, the specifications include (or are working on)
definitions for CL and BBS+ credentials. Within this community, there seems to
be some controversy as to the appropriate type of credentials to support.
According to a blog post%
\footnote{``Why the Verifiable Credentials Community Should Converge on BBS+'',
  \url{https://www.evernym.com/blog/bbs-verifiable-credentials/} (last
  access, January 15th, 2022).} by a cryptographer in Evernym (the company
that created Sovrin, which led to Indy) the complexity, engineering-wise, of a
verifiable credentials system with support to prove arbitrary claims on the
attributes of the credentials, makes it more desirable to restrict to
credentials supporting only selective disclosure%
\footnote{Interestingly, and confusingly, (parts of) this community equate BBS+
  credentials to selective disclosure, even though using BBS+ credentials does
  not (in theory) restrict the expressiveness of the claims that one can prove.
  This confusion seems to derive from the solution offered by the company MATTR,
  which has become one of the most popular proponents of BBS+ credentials
  restricted to selective disclosure.}
. Note that, related to the Verifiable Credentials effort, there are tens (maybe
even hundreds) of different initiatives that build credential systems claiming
to take into account privacy requirements (e.g., for healthcare use-cases, as a
consequence of the popular health passports originated from the COVID-19
pandemic). However, most of these initiatives lack formal, or even technical,
publicly accessible documentation, or have some public documentation but, as
of the moment of this writing, we are not aware of actual implementations
(like Microsoft's zero-knoweldge credentials%
\footnote{``Zero-knowledge credentials with deferred revocation checks'' white
  paper, available at \url{url{https://github.com/decentralized-identity/snark-credentials/blob/master/whitepaper.pdf}}
  (last access, January 15th, 2022.)}). Hence, we do not cover them here.

Finally, there are also related works that have seen real world deployments
which, although do not implement an anonymous credential systems, are somehow
influenced by them. Among these, we can find Cloudflare's PrivacyPass \cite{dgs+18},
which uses blind issuance of tokens associated to a secret key, through which
service providers can implement privacy-preserving blacklisting (in this sense,
they are closer to works like PEREA \cite{atk11} or Nymble \cite{tkcs11}, than
to anonymous credentials). A similar approach is followed by Whatsapp's DIT
system \cite{hij+21} (formerly known as PrivateStats), which further supports
the inclusion of attributes in the produced tokens. In this case, DIT is
designed to support privacy-preserving logging. Both in PrivacyPass and DIT, the
produced tokens are one-use, meaning that multiple uses of the same token are
linkable.

### 2022-01-15 prism-backend/research/soa_review/app-ac.tex
Added section on real-world deployments of ACs.

    build from an attribute-based VOPRF inspired by Naor and Reingold

@@

    resembles the usual ones for Anonymous Credentiasl (e.g., there is no

@@

>>>>

    built from an attribute-based VOPRF inspired by Naor and Reingold

@@

    resembles the usual ones for Anonymous Credentials (e.g., there is no

@@

\item Microsoft's zero-knowledge credentials \url{https://github.com/decentralized-identity/snark-credentials/blob/master/whitepaper.pdf}.
  \item The system presented by Microsoft is something that approximates
    anonymous credentials, but is not strictly an AC system. Note: this may just
    be because the authors do not properly model their proposal. It indeed
    follows an approach that resembles much the framework defined in \cite{cl01},
    where users have to establish pseudonyms with issuers and each RP, and can
    run presentations in which they prove that they have pseudonyms with both
    some issuer and the verifiying RP, such that the credential attributes
    associated to the issuer's pseudonym meet some claim. They further require
    some practical properties related to revocation: namely, deferred revocation
    and deferred revocation status check -- which are not very formally defined,
    though. They also make some informal claims about inherent limitations of
    these type of systems. Also, it is noteworthy that their proposal is one-show,
    although they sketch how to make it multi-show by relying on anonymous
    credentials. For expressiveness, they rely on ZK-SNARKS, and make some
    preliminary analysis based on popular choices of cryptographic algorithms.
\item Microsoft U-Prove \url{https://www.microsoft.com/en-us/research/publication/u-prove-technology-overview-v1-1-revision-2/}.
  \item Along with Idemix, U-Prove is probably the most mature application of
    ACs to date. It has both a solid scientific background, and seems that it
    reached a reasonably mature level implementation-wise.
  \item According to the technology overview report linked above, it supports
    the main functionalities for one-use ACs. Namely, it allows selective
    disclosure and blind issuance of attributes; as well as some of the also
    frequent variations, including several approaches for revocation, measures
    to desincentivize transferability, reuse-prevention, and scope-exclusive
    pseudonyms (note: most of these are natively provided by the system, and
    are even somehow related between themselves, like the reuse-prevention and
    the scope-exclusive pseudonyms). Integration with smartcards or similar
    trusted execution environments is also considered as a way to reach higher
    security in certain scenarios. However, this is an aspect that is not very
    formally treated even in \cite{bran00}, and is certainly a well-known source
    of complications, as learned from related works on DAA.
